The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-18 dit-paper_ieee.tex
spacing in formulas + ref to algorithm 1

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones,knuth1969art}. (note that $x^{-1} \; (mod
		\; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
		\begin{algorithm}
			\caption{Gauss's CRP Algorithm}
			\label{alg:algoCRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
				\REQUIRE $H$ is the hyperperiod of the system

@@

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
					\STATE $e_i \leftarrow (Mj \cdot invMj)$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{a_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}

>>>>

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli (Algorithm~\ref{alg:algoCRP}) \cite{gauss1965disquisitiones,knuth1969art}.
		(note that $x^{-1} \; (mod \; y)$ means the modular inverse of $x$ in the naturals modulo $y$)
		\begin{algorithm}
			\caption{Gauss's CRP Algorithm}
			\label{alg:algoCRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
				\REQUIRE $H$ is the hyperperiod of the system

@@

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
					\STATE $e_i \leftarrow Mj \cdot invMj$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{a_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}
